Pretty darn good control: when are approximate solutions better than approximate models

### 2023-01-06 manuscript/manuscript.Rmd
a bit more RL

@@

Reinforcement learning (RL) is a way of approaching *control problems* through machine learning.
An RL application can be conceptually separated into two parts: an *agent*, and an *environment*.
The *environment* is commonly a computer simulation.
The *agent*, on the other hand, is a computer program which interacts with the environment.
That is, the agent may act on the environment and change its state.
Such an action and its consequence, moreover, give the agent a *reward* which encodes our goal for the agent.
The main part of an RL algorithm is then to progressively improve the agent's *policy*, in order to maximize the cumulative reward received. 
This is done by aggregating experience and learning from it.

In our case, the environment will be a computational model of the population dynamics of a fishery.
The agent chooses how much to fish from a given species in the environment, thereby changing the populations in the environment's state.

\begin{align}
a^2+b^2=c^2
\end{align} -->

>>>>

# Fisheries: approximate models and approximate solutions

<!-- Introduce the 1D and 3D models, and have Figure 1 already here. -->

@@

Reinforcement learning (RL) is a way of approaching *control problems* through machine learning.
An RL application can be conceptually separated into two parts: an *agent*, and an *environment*.
The *environment* is commonly a computer simulation, although it sometimes can be a real world system.
The *agent*, on the other hand, is a computer program which interacts with the environment.
That is, the agent may act on the environment and change its state.
This, moreover, gives the agent a *reward* which encodes the control goal.
The main part of an RL algorithm is then to progressively improve the agent's *policy*, in order to maximize the cumulative reward received. 
This is done by aggregating experience and learning from it.
See Fig. \ref{tbd}.

In our case, the environment will be a computational model of the population dynamics of a fishery, with the environment state being a vector of all the fish populations, $S=(V_1, V_2, H)$.
The system evolves naturally according to \eqref{eq:3d model}.
At each time step, the agent harvests one of the populations, say $A$. 
Specifically, it chooses a quota $q$: the fraction of $A$ that will be fished.
This changes the state as
\begin{align*}
  (V_1,\ V_2,\ H) \mapsto ((1-q)V_1,\ V_2,\ H)
\end{align*}
and secures a reward of $qA$ to the agent.
Afterwards, the environment undergoes its natural dynamics.
